\begin{section}{Overview of the \cPanel API}
  
We introduce some of the core concepts and basic terminology for the \cPanel API.
    
  \begin{subsection}{Core Concepts}
    \begin{itemize}
    \item \define{Observer Pattern}
      \begin{itemize}
      \item The design pattern that the \cPanel API implements.
      \item Consists of two categories, {\em subjects} and {\em observers}.
      \item When the subject changes state, the registered observers are notified automatically.
      \item In \cPanel, the subjects are {\em hookable events} and the observers are {\em hooks}.
      \end{itemize}
    \item \define{Hookable Events}
      \begin{itemize}
      \item Specific points in \cPanel and \WHM where customized code can be executed.
      \item The \cPanel API provides an interface for writing code that works with \cPanel events.
      \item Examples include creation/removal of an account or the beginning/end of an update or backup.
      \item May permit the escalation of privileges.
      \item May force execution of hooks to run as a specific user.
      \item May permit a hook to block execution of further \cPanel code upon failure.
      \end{itemize}
    \item \define{Hooks}
      \begin{itemize}
      \item Customized code registered with a hookable event.
      \item Specified to run as a specific user on the system, defers to the event for privilege escalation.
      \item May be written as a script (perl/php) or a perl module.
      \end{itemize}
    \item \define{API1}
      \begin{itemize}
      \item Functions directly add/delete/modify data on the server.
      \item Data is printed directly to the \cPanel interface.
      \item Useful for writing skins or themes.
      \end{itemize}
    \item \define{API2}
      \begin{itemize}
      \item Functions return data structures that can be displayed to the browser or used in other scripts.
      \item These functions do not directly add/delete/modify data on the server.
      \item These data structures can be used via our XML API or through LivePHP/CGI scripts.
      \item A complete re-write of API1 with some functionality overlap.
      \end{itemize}
    \item \define{XML and JSON APIs}
      \begin{itemize}
      \item Generates output in XML or JSON format.
      \item Used when making calls to \cPanel functions in your own software.
      \item Returns data structures from API 1 or API 2 calls in XML/JSON format.
      \item Intended to be used remotely rather than directly on the server.
      \end{itemize}
    \item \define{Manage2 API}
      \begin{itemize}
      \item Provides mechanisms for retriviing/manipulating license information.
      \item Returns data in XML, JSON or YAML format.
      \end{itemize}
    \end{itemize}
  \end{subsection}

  \begin{subsection}{Anatomy of an API Call}
    
    %% TODO

  \end{subsection}

\end{section}

