\documentclass{beamer}

\usepackage{cpbeamer}

\title{Using Standardized Hooks}
\subtitle{A Gentle Introduction for cPanel Users}
\author{Charles Boyd}
\institute{cPanel, Inc.}
\date{cPanel Conference, 2012}
\subject{Standardized Hooks: Part 1}

\begin{document}

\frame{\titlepage}

\begin{frame}
  \frametitle{Introduction}
  \framesubtitle{What are we going to learn about?}
  \begin{itemize}
  \item What we are going to cover here:
    \begin{itemize}
    \item Basic concepts and goals of the Standardized Hooks framework.
    \item Extending the functionality of \WHM and \cPanel by example.
    \item Customizing how \WHM and \cPanel handle events.
    \end{itemize}
  \item What we are {\em not} going to cover here:
    \begin{itemize}
    \item Technical details about the design of the \cPanel API.
    \item How to extend the functionality of the \cPanel API.
    \item Other advanced topics.
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Introduction}
  \framesubtitle{Who is this presentation for?}
  \begin{itemize}
  \item Individuals, Companies and Organizations who use \cPanel as their hosting platform.
  \item System administrators who work with \cPanel servers and want to add custom functionality.
  \item Software Developers who want to integrate their code into \cPanel.
  \item Anybody who wants to learn how make \cPanel do more than it already does.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Introduction}
  \frametitle{What should you already know?}
  \begin{itemize}
  \item How to do common administrative tasks in \WHM and \cPanel.
  \item How to use the command line on a GNU/Linux (or FreeBSD) server.
  \item Knowledge of Perl will be useful but not necessary.
  \end{itemize}
\end{frame}

\end{document}
